SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-02-16 scipy-1.0/paper.tex
ENH: intro: adding back LIGO example GW150914-Python seemed like a weak reference, and the link between SciPy and the published LIGO results is already established, so I removed it. Added another example of LIGO results that used SciPy via PyCBC.

SciPy is a library of numerical routines for the Python programming
language that provides fundamental building blocks for modeling and
solving scientific problems. 
// For example, when LIGO, the Laser
Interferometer Gravitational-Wave Observatory, recently announced the
discovery of gravitational waves, their published Python analysis
scripts\cite{LIGO-open,alex_nitz_2018_1596771,GW150914-Python,
PhysRevD.93.122003} imported many different SciPy submodules for:
signal processing, interpolation, input / output, optimization, statistics,
integration, and more.
SciPy has routines for the numerical solution of problems from classes
including linear systems, integration, differential equations, eigenvalue 
problems, and interpolation; it also provides
specialized data structures, such as sparse arrays and k-dimensional
trees. SciPy is built on top of NumPy\cite{vanderwalt2011numpy,Oliphant-2015},
which provides array data structures and related fast numerical routines, and
SciPy is itself the foundation upon which higher level scientific libraries,
including scikit-learn\cite{pedregosa2011scikit}
and scikit-image\cite{vanderwalt2014scikit}, are built.

>>>>

SciPy is a library of numerical routines for the Python programming
language that provides fundamental building blocks for modeling and
solving scientific problems. 
SciPy has routines for the numerical solution of problems from classes
including linear systems, integration, differential equations, eigenvalue 
problems, and interpolation; it also provides
specialized data structures, such as sparse arrays and k-dimensional
trees. SciPy is built on top of NumPy\cite{vanderwalt2011numpy,Oliphant-2015},
which provides array data structures and related fast numerical routines, and
SciPy is itself the foundation upon which higher level scientific libraries,
including scikit-learn\cite{pedregosa2011scikit}
and scikit-image\cite{vanderwalt2014scikit}, are built. 
SciPy is relied upon by scientists, engineers, and others 
around the world. For example, the 
scripts\cite{alex_nitz_2018_1596771, LIGO-open}
used in the analysis of gravitational waves
\cite{PhysRevD.93.122003, abbott2017gw170817} 
import several submodules of SciPy.
